The Dynamics of Anthropomorphic Effects in Human-Robot Interaction

### 2014-03-21 paper.tex
latest changes in the domino study part

\begin{itemize}
	\item \textit{Life-likeness}, uch as being alive or having (parts of) a body, \eg \textit{``she can be reborn since you copied her memory stick''};
	\item \textit{Emotional states} or the technology having a feeling, \eg \textit{``oh no, poor AIBO''};
	\item \textit{Gender, personality} or the technology having an \textit{intention}, \eg Roomba \textit{``seems to like to hang around under the sofa''};
	\item When the author gave the technology a \textit{name}, \eg \textit{``whenever I show Java his pink ball''};
	\item Being \textit{socially integrated}, such as being a family member, \eg \textit{``I'm considering adding a Roomba to the family''};
	\item \textit{Metaphorical ways}, \eg Roomba \textit{``sings its victory song when it finishes and docks''}.
\end{itemize}

@@

>>>>

\begin{itemize}
	\item \textit{Life-likeness}, uch as being alive or having (parts of) a body, \eg \textit{``she can be reborn since you copied her memory stick''};
	\item \textit{Emotional states, empathy} or the technology having a \textit{feeling}, \eg \textit{``oh no, poor AIBO''};
	\item \textit{Gender, personality} or the technology having an \textit{intention}, \eg Roomba \textit{``seems to like to hang around under the sofa''};
	\item When the author gave the technology a \textit{name}, \eg \textit{``whenever I show Java his pink ball''};
	\item Being \textit{socially integrated}, such as being a family member, \eg \textit{``I'm considering adding a Roomba to the family''};
	\item \textit{Metaphorical ways}, \eg Roomba \textit{``sings its victory song when it finishes and docks''}.
\end{itemize}

@@

The so-called "Ranger domino study" describes a child-robot interaction study that we carried out in a fairly controlled lab setting. One of the goals of this study was to investigate the effect of unexpected robot behavior on (1) the interaction and engagement with robot, and (2) how far children would ascribe human-like abilities (\eg intentions, cognitive abilities) to the robot.
13 groups of each two children (n = 26) who were all between 4-5 years old and knew each other, were invited to play for around 20 minutes with the Ranger robot toy box \citep{fink2014which} and assemble a domino together. The robot was operated by one of the experimenters using the wizard-of-oz technique. Ranger was supposed to transport domino tiles between the two children and it would do its job correctly for the first 7 domino tiles. Then, however, the robot started misbehaving by either \textit{disobeying} to the child
